Papers

### 2025-12-12 papers.qmd
update

-   Stafford, T. and Dewar, M. (2014). [Tracing the trajectory of skill learning with a very large sample of online game players](http://pss.sagepub.com/content/25/2/511). Psychological Science, 25(2) 511--518. See also: [Data and analysis code](https://github.com/tomstafford/axongame).

>>>>

-   Stafford, T. and Dewar, M. (2014). [Tracing the trajectory of skill learning with a very large sample of online game players](https://doi.org/10.1177/0956797613511466). Psychological Science, 25(2) 511--518. <https://doi.org/10.1177/0956797613511466> See also: [Data and analysis code](https://github.com/tomstafford/axongame).
